Maybe Slipstreams

### 2014-03-11 paper.tex
Suppress numbering on abstract

\section{Abstract}
We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world. We allow signal networks to be dynamic by modeling them as higher-order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe. All signal values are modeled as $Maybe$ values to allow for defined behavior in the face of disrupted signals, and to reference signal values before they have any reasonable value. We also specify a DSL that uses this FRP model, allowing a programmer to easily design signal networks to accomplish tasks by specifying layers and how the layers interact. Our implementation builds on previous work by being more practical. The DSL arises naturally from our definition of FRP, is simple to use and requires only limited knowledge of the underlying FRP concepts.

>>>>

\section*{Abstract}
We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world. We allow signal networks to be dynamic by modeling them as higher-order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe. All signal values are modeled as $Maybe$ values to allow for defined behavior in the face of disrupted signals, and to reference signal values before they have any reasonable value. We also specify a DSL that uses this FRP model, allowing a programmer to easily design signal networks to accomplish tasks by specifying layers and how the layers interact. Our implementation builds on previous work by being more practical. The DSL arises naturally from our definition of FRP, is simple to use and requires only limited knowledge of the underlying FRP concepts.
